### 2024-11-08 README.Rmd
embeddings stay embeddings + fixed color printing
bug fixes and examples

Common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). Includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. 'GloVe'), applying them to words, aggregating to produce text embeddings, and reducing dimensionality.

@@

embeddingplyr is model agnostic; it can be used to work with embeddings from decontextualized models like [GloVe](https://nlp.stanford.edu/projects/glove/) and [word2vec](https://code.google.com/archive/p/word2vec/), or from contextualized models like BERT or others made available through the [text](https://r-text.org) package.

@@

The outcome is an "embeddings" object. An embeddings object is just a numeric matrix with tokens as rownames. This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `predict.embeddings()` and `find_nearest()`:

@@

find_nearest(glove_twitter_25d, "dog", 5L)
```

>>>>

Common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). Includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. [GloVe](https://nlp.stanford.edu/projects/glove/)), applying them to words, aggregating to produce text embeddings, and reducing dimensionality.

@@

embeddingplyr is model agnostic; it can be used to work with embeddings from decontextualized models like [GloVe](https://nlp.stanford.edu/projects/glove/) and [word2vec](https://code.google.com/archive/p/word2vec/), or from contextualized models like BERT or others made available through the '[text](https://r-text.org)' package.

@@

The outcome is an embeddings object. An embeddings object is just a numeric matrix with tokens as rownames. This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `predict.embeddings()` and `find_nearest()`:

@@

find_nearest(glove_twitter_25d, "dog", 5L, sim_func = cos_sim)
```
